Trending assessment for nowcasts, measurements, and forecasts

### 2024-03-07 sections/01-introduction.tex
Update on Overleaf.

Measurement, prediction, and forecasting methods are becoming increasingly important and sophisticated in a world of fast-developing technologies and increasing data availability. While introducing new medical measurement methods requires a comprehensive evaluation and comparison with established standard measurement methods to ensure their validity and reliability, it is generally essential for forecasts and nowcasting methods to assess the extent to which the predictions correspond to the development of reality. Conventionally, the methods are evaluated using distance measures that take aggregated local absolute differences between predictions (or measurements) and target values into account. For example, the Continuous Ranked Probability Score (CRPS) can be used to evaluate the accuracy of probabilistic predictions. It is also based on the integrated squared differences between the cumulative distribution function (CDF) of the prediction and the Heaviside jump function. These measures all fail to consider whether the right direction of change is being taken, which can often be highly relevant in practice. The information about whether an estimator, be it a measurement device, forecast, or nowcast, can accurately predict an increase or decrease is crucial when taking  of development of the actual value on the basis of the estimator's prediction results. In the following, we first provide an overview of the characteristics and evaluations of the three areas: Measurement, Prediction and Nowcasting and their relationship with Trending.

>>>>

Measurement, prediction, and forecasting methods are becoming increasingly important and sophisticated in a world of fast-developing technologies and increasing data availability. While introducing new medical measurement methods requires a comprehensive evaluation and comparison with established standard measurement methods to ensure their validity and reliability, it is generally essential for forecasts and nowcasting methods to assess the extent to which the predictions correspond to the development of reality. Conventionally, the methods are evaluated using distance measures that take aggregated local absolute differences between predictions (or measurements) and target values into account. For example, the Continuous Ranked Probability Score (CRPS) can be used to evaluate the accuracy of probabilistic predictions. It is also based on the integrated squared differences between the cumulative distribution function (CDF) of the prediction and the Heaviside jump function. These measures all fail to consider whether the right direction of change is being taken, which can often be highly relevant in practice. The information about whether an estimator, be it a measurement device, forecast, or nowcast, can accurately predict an increase or decrease is crucial when taking desi of development of the actual value on the basis of the estimator's prediction results. In the following, we first provide an overview of the characteristics and evaluations of the three areas: Measurement, Prediction and Nowcasting and their relationship with Trending.
